SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-13 scipy-1.0/paper.tex

In terms of software systems and architecture, SciPy's scope matches NumPy's:
algorithms for in-memory computing on single machines, with support for a wide
range of data types and process architectures. Distributed computing and support
for graphics processing units (GPUs) were explicitly out of scope at the 1.0
release point, but this has been revised in our roadmap at the time of writing
(see below).

>>>>

In terms of software systems and architecture, SciPy's scope matches NumPy's:
algorithms for in-memory computing on single machines, with support for a wide
range of data types and process architectures. Distributed computing and support
for graphics processing units (GPUs) were explicitly out of scope at the 1.0
release point, but this has been revised in our roadmap at the time of writing
(see Discussion).
